---
title: "Slim_simulations_TSR_lasting"
output: html_document
---

## Load SliM outputs into R
```{r}
library(readr)
Simulations_all <- read_table2("˜/All_runs_42000_0.5.txt", col_names=FALSE)

colnames(Simulations_all) [2] <- "Generation"
colnames(Simulations_all) [8] <- "Sel_Coeff"

# Generate relevant analysis parameters
Simulations_all$Allele_freq <- Simulations_all$X12/84000

Simulations_all$Run <- sapply(strsplit(as.character(Simulations_all$X1), "[.]"), "[", 3)

Simulations_all$Mut_freq <- as.numeric(paste(0, sapply(strsplit(as.character(Simulations_all$X1), "[.]"), "[", 5 ), sep='.'))  

Simulations_all$Run_Identifier <- paste(Simulations_all$Run, Simulations_all$Mut_freq, Simulations_all$Sel_Coeff, sep = "_")
Simulations_all$Sel_Coeff <- as.factor(Simulations_all$Sel_Coeff)

# Create unique identifier
Simulations_all$Unique_Identifier <- paste(Simulations_all$Run, Simulations_all$Generation, Simulations_all$Mut_freq, Simulations_all$Sel_Coeff, sep="_")

# Get an idea when the values plateau
hist(Simulations_all$Generation)

# Cut data at 1000 Generations
Simulations_all_1000 <- subset(Simulations_all, Generation <= 1000)
Simulations_all_1000
```

## Generate dataframe from 1 to 1,000 for all Runs (in case the mutation was lost, the data generation is stopped. In this case, we need to fill it up with 0s to calculate mean values and confidence intervals)
```{r}
# Generation of an base data frame
base_df1 <- data.frame( Sel_Coeff = rep(c(0, -0.05, -0.1, -0.2, -0.3, -0.4), times = 4), Mut_freq = rep(c(0.05, 0.1, 0.4, 0.7), each = 6))
  
# Repeat data frame as many runs needed
base_df2 <- base_df1[rep(seq_len(nrow(base_df1)), each = 400), ]
# Add Run column
base_df2$Run <- rep(seq(1:400), times = 24)

# Repeat data frame as many generations needed
base_df3 <- base_df2[rep(seq_len(nrow(base_df2)), each = 1000), ]
# Add Generation column
base_df3$Generation <- rep(seq(1:1000), times = 4*6*400)

# Unique identifier per row
base_df3$Unique_Identifier <- paste(base_df3$Run, base_df3$Generation, base_df3$Mut_freq, base_df3$Sel_Coeff, sep="_")
head(base_df3)

# Merge with real data
Simulations_complete <- merge(base_df3, Simulations_all_1000, by = "Unique_Identifier", all = TRUE)

# Convert NA's to 0's
Simulations_complete$Allele_freq <- sapply(Simulations_complete$Allele_freq, FUN = function(x){if(is.na(x)){x<-0}else{x<-x}})

Simulations_complete
Simulations_complete1 <- Simulations_complete[ ,c(1,2,3,4,5,18,21)]
Simulations_complete1$Sel_Coeff.x <- factor(Simulations_complete1$Sel_Coeff.x, levels = c("0", "-0.05", "-0.1", "-0.2","-0.3", "-0.4"))
Simulations_complete1
```

## Calculate mean values
```{r}
sim_mean <- aggregate(Simulations_complete1$Allele_freq , by=list(Simulations_complete1$Generation.x, Simulations_complete1$Sel_Coeff.x, Simulations_complete1$Mut_freq.x), FUN = mean)

colnames(sim_mean) <- c('Generation',  'Sel_Coeff', 'Mut_freq', 'Mean')

sim_mean
```

## Calculate confidence intervals, default 0.95 (Attention: Calculation takes several hours!)
```{r}
# There is no variation in the first generation, therefore first generation is removed for this calculation.

# Remove first generation
Simulations_complete_subset_ <- subset(Simulations_complete1, Generation.x > 1)

# Calculate confidence intervals
library(rcompanion)
confis <- groupwiseMean(data = Simulations_complete_subset_,
              var         = "Allele_freq",
              group       = c("Generation.x", "Sel_Coeff.x", "Mut_freq.x"),
              traditional = FALSE,
              percentile  = TRUE, na.rm = TRUE)
                                   

save.image(file = "Simulations_TSR_lasting.RData")
```

## Subset mean for allele frequency 0 to know the generation, in which the mutation is lost.
```{r}
sim_mean

mean_0 <- subset(sim_mean, Mean == 0)
mean_0

aggregate(mean_0$Generation, list(mean_0$Sel_Coeff, mean_0$Mut_freq), min)
```

## Subset for each TSR frequency to plot them individually
```{r}
confis
confis_0.05 <- subset(confis, Mut_freq.x == 0.05)
confis_0.1 <- subset(confis, Mut_freq.x == 0.1)
confis_0.4 <- subset(confis, Mut_freq.x == 0.4)
confis_0.7 <- subset(confis, Mut_freq.x == 0.7)
```

## Combined plot for all allele frequencies
```{r}
library(ggplot2)

p2 <- ggplot(data=confis, aes(x=Generation.x, y=Mean , group=Sel_Coeff.x)) + facet_grid(. ~ Mut_freq.x) + 
  geom_ribbon(aes(ymin = Percentile.lower, ymax = Percentile.upper, fill=Sel_Coeff.x), alpha = 0.3) +
  geom_line(aes(y = Mean, x = Generation.x, color = Sel_Coeff.x )) + ylim(0,0.8) + xlab("Generation") +ylab("Allele frequency") + coord_cartesian(xlim=c(0,300)) +scale_colour_manual(name="Sel. coefficient",values=c("#bd0026","#252525", "#969696","#f1b6da","#e6b800","#d9d9d9"))  +scale_fill_manual(name="Sel. coefficient",values=c("#bd0026","#252525", "#969696","#f1b6da","#e6b800","#d9d9d9")) + guides(color = guide_legend(override.aes = list(size = 3))) + theme_light() + theme(text=element_text(size=20))
p2

png(file = "Allele_freq_TSR_lasting.png" ,  width = 600, height = 150, units='mm', res = 300)
  print(p2)
dev.off()
  

pdf(file = "Allele_freq_TSR_lasting.pdf" , width = 20, height = 5)
  print(p2)
dev.off()

```

## Allele freq = 0.7
```{r}
p3 <- ggplot(data=confis_0.7, aes(x=Generation.x, y=Mean , group=Sel_Coeff.x)) + 
  geom_ribbon(aes(ymin = Percentile.lower, ymax = Percentile.upper, fill=Sel_Coeff.x), alpha = 0.3) +
  geom_line(aes(y = Mean, x = Generation.x, color = Sel_Coeff.x), size=0.8) + ylim(-0.15,0.8) + xlab("Generation") +ylab("Allele frequency") + coord_cartesian(xlim=c(0,300)) +scale_colour_manual(name="Sel. coefficient",values=c("#bd0026","#252525", "#969696","#f1b6da","#e6b800","#d9d9d9"))  +scale_fill_manual(name="Sel. coefficient",values=c("#bd0026","#252525", "#969696","#f1b6da","#e6b800","#d9d9d9")) + guides(color = guide_legend(override.aes = list(size = 3))) + theme_light() + theme(text=element_text(size=18)) +
  geom_segment(aes(x = 351, y = -0.1, xend = 351, yend = 0), linetype="dashed", size=0.3, color="#969696") + annotate("text", x = 351, y = -0.15, label = "351", size = 5.5, color="#969696") +
  geom_segment(aes(x = 155, y = -0.1, xend = 155, yend = 0), linetype="dashed", size=0.3, color="#f1b6da") + annotate("text", x = 155, y = -0.15, label = "155", size = 5.5, color="#f1b6da") +
  geom_segment(aes(x = 101, y = -0.1, xend = 101, yend = 0), linetype="dashed", size=0.3, color="#e6b800") + annotate("text", x = 110, y = -0.15, label = "101", size = 5.5, color="#e6b800") +
  geom_segment(aes(x = 86, y = -0.1, xend = 86, yend = 0), linetype="dashed", size=0.3, color="#d9d9d9") + annotate("text", x = 75, y = -0.15, label = "86", size = 5.5, color="#d9d9d9") 

p3

png(file = "Allele_freq_TSR_lasting_0.7.png" ,  width = 140, height = 80, units='mm', res = 300)
  print(p3)
dev.off()
  

pdf(file = "Allele_freq_TSR_lasting_0.7.pdf" , width = 5.5, height = 3)
  print(p3)
dev.off()

```

## Allele freq = 0.4
```{r}
p4.b <- ggplot(data=confis_0.4, aes(x=Generation.x, y=Mean , group=Sel_Coeff.x)) + 
  geom_ribbon(aes(ymin = Percentile.lower, ymax = Percentile.upper, fill=Sel_Coeff.x), alpha = 0.3) +
  geom_line(aes(y = Mean, x = Generation.x, color = Sel_Coeff.x), size=0.8 ) + ylim(-0.07,0.5) + xlab("Generation") +ylab("Allele frequency") + coord_cartesian(xlim=c(0,300)) +scale_colour_manual(name="Sel. coefficient",values=c("#bd0026","#252525", "#969696","#f1b6da","#e6b800","#d9d9d9"))  +scale_fill_manual(name="Sel. coefficient",values=c("#bd0026","#252525", "#969696","#f1b6da","#e6b800","#d9d9d9")) + guides(color = guide_legend(override.aes = list(size = 3))) + theme_light() + theme(text=element_text(size=18)) + 
  geom_segment(aes(x = 258, y = -0.04, xend = 258, yend = 0), linetype="dashed", size=0.3, color="#969696") + annotate("text", x = 258, y = -0.07, label = "258", size = 5.5, color="#969696") +
  geom_segment(aes(x = 151, y = -0.04, xend = 151, yend = 0), linetype="dashed", size=0.3, color="#f1b6da") + annotate("text", x = 151, y = -0.07, label = "151", size = 5.5, color="#f1b6da") +
  geom_segment(aes(x = 105, y = -0.04, xend = 105, yend = 0), linetype="dashed", size=0.3, color="#e6b800") + annotate("text", x = 105, y = -0.07, label = "105", size = 5.5, color="#e6b800") +
  geom_segment(aes(x = 68, y = -0.04, xend = 68, yend = 0), linetype="dashed", size=0.3, color="#d9d9d9") + annotate("text", x = 68, y = -0.07, label = "68", size = 5.5, color="#d9d9d9") 

p4.b

png(file = "Allele_freq_TSR_lasting_0.4_ylim.png" ,  width = 140, height = 80, units='mm', res = 300)
  print(p4.b)
dev.off()
  

pdf(file = "Allele_freq_TSR_lasting_0.4_ylim.pdf" , width = 5.5, height = 3)
  print(p4.b)
dev.off()
```

## Allele freq = 0.1
```{r}
p5.b <- ggplot(data=confis_0.1, aes(x=Generation.x, y=Mean , group=Sel_Coeff.x)) + 
  geom_ribbon(aes(ymin = Percentile.lower, ymax = Percentile.upper, fill=Sel_Coeff.x), alpha = 0.3) +
  geom_line(aes(y = Mean, x = Generation.x, color = Sel_Coeff.x), size=0.8 ) + ylim(-0.02,0.12) + xlab("Generation") +ylab("Allele frequency") + coord_cartesian(xlim=c(0,300)) +scale_colour_manual(name="Sel. coefficient",values=c("#bd0026","#252525", "#969696","#f1b6da","#e6b800","#d9d9d9"))  +scale_fill_manual(name="Sel. coefficient",values=c("#bd0026","#252525", "#969696","#f1b6da","#e6b800","#d9d9d9")) + guides(color = guide_legend(override.aes = list(size = 3))) + theme_light() + theme(text=element_text(size=18)) + 
  geom_segment(aes(x = 261, y = -0.01, xend = 261, yend = 0), linetype="dashed", size=0.3, color="#969696") + annotate("text", x = 261, y = -0.02, label = "261", size = 5.5, color="#969696") +
  geom_segment(aes(x = 114, y = -0.01, xend = 114, yend = 0), linetype="dashed", size=0.3, color="#f1b6da") + annotate("text", x = 132, y = -0.02, label = "114", size = 5.5, color="#f1b6da") +
  geom_segment(aes(x = 86, y = -0.01, xend = 86, yend = 0), linetype="dashed", size=0.3, color="#e6b800") + annotate("text", x = 97, y = -0.02, label = "86", size = 5.5, color="#e6b800") +
  geom_segment(aes(x = 78, y = -0.01, xend = 78, yend = 0), linetype="dashed", size=0.3, color="#d9d9d9") + annotate("text", x = 68, y = -0.02, label = "78", size = 5.5, color="#d9d9d9") 

p5.b

png(file = "Allele_freq_TSR_lasting_0.1_ylim.png" ,  width = 140, height = 80, units='mm', res = 300)
  print(p5.b)
dev.off()
  

pdf(file = "Allele_freq_TSR_lasting_0.1_ylim.pdf" , width = 5.5, height = 3)
  print(p5.b)
dev.off()
```

## Allele freq = 0.05
```{r}
p6.b <- ggplot(data=confis_0.05, aes(x=Generation.x, y=Mean , group=Sel_Coeff.x)) + 
  geom_ribbon(aes(ymin = Percentile.lower, ymax = Percentile.upper, fill=Sel_Coeff.x), alpha = 0.3) +
  geom_line(aes(y = Mean, x = Generation.x, color = Sel_Coeff.x), size=0.8 ) + ylim(-0.009,0.06) + xlab("Generation") +ylab("Allele frequency") + coord_cartesian(xlim=c(0,300)) + scale_colour_manual(name="Sel. coefficient",values=c("#bd0026","#252525", "#969696","#f1b6da","#e6b800","#d9d9d9"))  +scale_fill_manual(name="Sel. coefficient",values=c("#bd0026","#252525", "#969696","#f1b6da","#e6b800","#d9d9d9")) + guides(color = guide_legend(override.aes = list(size = 3))) + theme_light() + theme(text=element_text(size=18)) + 
  geom_segment(aes(x = 258, y = -0.005, xend = 258, yend = 0), linetype="dashed", size=0.3, color="#969696") + annotate("text", x = 258, y = -0.009, label = "258", size = 5.5, color="#969696") +
  geom_segment(aes(x = 117, y = -0.005, xend = 117, yend = 0), linetype="dashed", size=0.3, color="#f1b6da") + annotate("text", x = 129, y = -0.009, label = "117", size = 5.5, color="#f1b6da") +
  geom_segment(aes(x = 104, y = -0.005, xend = 104, yend = 0), linetype="dashed", size=0.3, color="#e6b800") + annotate("text", x = 88, y = -0.009, label = "104", size = 5.5, color="#e6b800") +
  geom_segment(aes(x = 62, y = -0.005, xend = 62, yend = 0), linetype="dashed", size=0.3, color="#d9d9d9") + annotate("text", x = 54, y = -0.009, label = "62", size = 5.5, color="#d9d9d9") 

p6.b

png(file = "Allele_freq_TSR_lasting_0.05_ylim.png" ,  width = 140, height = 80, units='mm', res = 300)
  print(p6.b)
dev.off()
  

pdf(file = "Allele_freq_TSR_lasting_0.05_ylim.pdf" , width = 5.5, height = 3)
  print(p6.b)
dev.off()
```
